Manuscript draft

### 2019-06-07 manuscript/manuscript draft.Rmd
updated manuscript draft

| Database | Variables downloaded | Citation |
|---------------|-------------------------------------------------|-------------------|
| WorldClim | Mean annual temperature; temperature seasonality; annual temperature range; mean annual precipitation | [@Hijmans2005] |
| WorldClim2 | Vapour pressure; solar radiation | [@Fick2017] |
| Climate Research Unit (CRU) time-series dataset v 4.03 | Cloud cover; annual frost days; annual wet days; potential evapotranspiration | [@Harris2014] |
| Global Aridity Index and Potential Evapotranspiration Climate Database | Aridity; potential evapotranspiration | [@Trabucco2018] |
| TerraClimate | Vapour pressure deficit | [@Abatzoglou2018] |

@@

>>>>

| Database | Variables downloaded | Citation |
|-----------------------|--------------------------------------------|---------------------|
| WorldClim | Mean annual temperature; temperature seasonality; annual temperature range; mean annual precipitation | [@Hijmans2005] |
| WorldClim2 | Vapour pressure; solar radiation | [@Fick2017] |
| Climate Research Unit (CRU) time-series dataset v 4.03 | Cloud cover; annual frost days; annual wet days; potential evapotranspiration | [@Harris2014] |
| Global Aridity Index and Potential Evapotranspiration Climate Database | Aridity; potential evapotranspiration | [@Trabucco2018] |
| TerraClimate | Vapour pressure deficit | [@Abatzoglou2018] |

@@

###References
